On the performance of the MAC model

### 2018-11-01 2018_nips_vigil/mac.tex
clean up - intro + mac
Shorteninf of MAC section, picked several experiment results from table 2

The MAC network~\cite{hudson2018compositional} is a recurrent model that performs reasoning 
using multiple steps, where each step involves sequentially analyzing a part of the question following which attention on the image is changed suitably.
At the end, a suitable answer is given based on this composite reasoning.
To improve the accuracy of prediction, both the questions and images
are preprocessed suitably. For the question,  a word-embedding is first used to
transformed the question into a sequence of vectors which is then passed through
a bidirectional LSTM to produce a sequence of hidden state pairs. Each such pair 
corresponds to a unique word in the question and is called the 
\emph{contextual embedding} for that word.
Similarly each image is initially processed using a pre-trained network (using ResNet) followed by two trainable CNN layers.

@@

The core of the network is a sequence of recurrent MAC cells. A MAC cell (Figure 1) is performing one reasoning step. At every step the network is driving the attention on one part of the question and the corresponding part of the image. This operation is made possible by the combination of 3 units working together, a control unit, a read and a write units. The control unit is updating the control state and drives the attention over the question. Given this control state, the read unit then retrieves information from the memory and drives the attention over the image.
Finally, the write unit retrieves this visual information and updates the memory state.
The last part of the network is the output unit. The output unit is simply a classifier that process the concatenation of the question representation and the final memory to produce a final answer.

By going through this recurrent process, the network performs a reasoning strategy that learns concepts and relations between them. MAC is performing state of the art accuracy on CLEVR and CLEVR Humans datasets.
In contrast to modular approaches \cite{andreas2016learning,hu2017learning,johnson2017inferring}, MAC is fully
differentiable and does not require additional supervision. It is making use of a single computational cell chained in sequence rather than a collection of custom modules deployed in a rigid tree structure.
In contrast to augmented CNN approaches, the MAC model provides an ability for relational reasoning with better generalization capacity, higher
computational efficiency and enhanced transparency \cite{hudson2018compositional}.

>>>>

@@

The MAC network~\cite{hudson2018compositional} is a recurrent model that performs sequential reasoning, where each step involves analyzing a part of the question followed by shifting of attention over the image.
The core of the model is the MAC cell, supported with an input unit that processes question and image pair, and output unit which produces the answer.% (a two layer MLP).
The input unit  uses an LSTM~\cite{hochreiter1997long} to process the question in a word-by-word manner producing a sequence of \emph{contextual words} and a final \emph{question representation}.
Besides, the input unit utilizes a pre-trained ResNet~\cite{he2016resnet} followed by two CNN layers to extract a feature map (referred to as \emph{knowledge base}) from the image.

The MAC cell consists of a control unit, a read unit and a write unit (\Fig{fig:mac_cell}).
The control unit is updating the control state $c_i$ and drives the attention over the list of \emph{contextual words} $cw$ taking into account the \emph{question representation} $q$.
Guided by $c_i$,  the read unit extracts information from the \emph{knowledge base} $KB$ and combines it with the previous memory state $m_{i-1}$  to produce the \emph{read vector} $r_i$.
Finally, the write unit integrates $r_i$ and $m_{i-1}$ to update the memory state.

%The MAC network reached state-of-the-art accuracy on the CLEVR dataset.
%In contrast to augmented CNN approaches, the MAC model provides an ability for relational reasoning with better generalization capacity, higher computational efficiency and enhanced transparency.

%In contrast to modular approaches \cite{andreas2016learning,hu2017learning,johnson2017inferring}, MAC is fully differentiable and does not require additional supervision.
